Gradual Soundness: Lessons from Static Python

### 2022-01-13 pj-7.1/paper.tex
pj: some thoughts in the conclusion

In conclusion, we summarize the

>>>>

\SP{} is ambitious in many ways:
\begin{itemize}
  \item Type checker and compiler for Python syntax
  \item Fork of Python 3.8
  \item Add significant runtime components: vtable, classloader
  \item Add a method-based JIT
  \item Aiming for tens of thousands of typed modules (surely not all 45k in the server, but otoh the plan must be to hit other parts of IG too)
\end{itemize}

But \SP{} is also carefully targeted:
\begin{itemize}
  \item
    Not aiming for an exhaustive type checker.
    The availability of tools like Pyre already do a fine job.
    (Don't forget that consequently, it's helpful for undefined types go to dynamic.)
  \item
    Shallow types come first in the implementation, then concrete / checked
    (ditto for adoption)
  \item
    Not aiming for the full gradual guarantees.
    Only really matters for the initial migration, the common case.
    Indeed, it's important to not have the guarantee for primitives for their performance.
  \item
    The type checker is module-at-a-time, not fine-grained.
\end{itemize}
